NFC and burnout in teachers - A replication and extension study

### 2021-11-29 Manuscript/Manuscript.Rmd
fixed knitting bugs and renamed tables and plots

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by the findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady 2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

@@

```{r scores, echo=FALSE, message=FALSE, warning=FALSE}

@@

    met_table <-
      kbl(desc_met,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote

@@

```{r desc_table, echo=FALSE, message=FALSE, warning=FALSE}

  desc_table <-
  kbl(correlations,
      booktabs = TRUE, # no vertical lines
      escape = FALSE, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = FALSE, # correctly print special characters
             threeparttable = TRUE) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

Basic metric descriptives of the questionnaire scores and subscales are listed in **Table 1**.
Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Roesseel2012].
Correlations and internal consistencies are displayed in **Table 2**.
For this descriptive analysis, the variables DTH, DTL, and DRF were computed as a sum of their item scores, not weighted as in the structural equation model.
Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman"), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman"), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman"), format = "rmarkdown")`).
The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.

`r desc_table`

@@

  fit_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  fit_table[2:ncol(fit_table)] <- format(round(fit_table[2:ncol(fit_table)], digits = 3), nsmall = 2)

  replication_table <-
    kbl(fit_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edgeLabels = fit_param, # specify the edge labels with the asterisks as previously created
                       edge.label.cex = 1, esize = 2, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

@@

In order to replicate findings by Grass et al. [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "c1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "c1"], digits = 3)`), which was not the case in the study by Grass et al. [-@Grass2018].

@@

  fityears_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC and years spent teaching $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  fityears_table[2:ncol(fityears_table)] <- format(round(fityears_table[2:ncol(fityears_table)], digits = 3), nsmall = 2)

  replicationyears_table <-
    kbl(fityears_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 9, 11) %>%
    pack_rows("Total Effect", 12, 12) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```

@@

  fityears_plot <- semPaths(fityears, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edge.label.cex = 1, esize = 2, # size specifications
                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       exoCov = FALSE, # do not plot covariance between exogenous variables
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

@@

  fit2_plot <- semPaths(fit2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```
```{r fit2_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  fit2_table[2:ncol(fit2_table)] <- format(round(fit2_table[2:ncol(fit2_table)], digits = 3), nsmall = 2)

  drrmodel_table <-
    kbl(fit2_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```

>>>>

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by the findings that NFC is negatively associated with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and teacher trainees [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by reappraisal, active and passive coping, but not by suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor.
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

@@

```{r scores, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

@@

    Table1 <-
      kbl(desc_met,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote

@@

```{r correlations_table, echo=FALSE, message=FALSE, warning=FALSE}

  Table2 <-
  kbl(correlations,
      booktabs = TRUE, # no vertical lines
      escape = FALSE, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = FALSE, # correctly print special characters
             threeparttable = TRUE) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

Basic metric descriptives of the questionnaire scores and subscales are listed in **Table 1**.
Only the ERQ sum score and its Reappraisal subscale followed a multivariate normal distribution, so the results of the models should be interpreted with some caution and with a focus on indices that are robust against violation of normality, such as the Satorra-Bentler or Yuan-Bentler-scaled test statistics [@Rosseel2012].

`r Table1`

Correlations and internal consistencies are displayed in **Table 2**.
For this descriptive analysis, the variables DTH, DTL, and DRF were computed as a sum of their item scores, not weighted as in the structural equation model.
Using traditional cut-off values [@Nunnally1994], the Cronbach's Alpha of the three demand-resource-ratios can be considered *acceptable*.
The more robust MacDonald's Omega [@Dunn2014] did not deviate much from Cronbach's Alpha and indicated *acceptable* to *good* internal consistency.
As expected, the MBI score was positively correlated with DTH (`r cor_apa(cor.test(score_data$mbi, score_data$dth, method = "spearman"), format = "rmarkdown")`) and negatively with DRF (`r cor_apa(cor.test(score_data$mbi, score_data$drf, method = "spearman"), format = "rmarkdown")`), large associations according the classification scheme by Gignac and Szodorai [-@Gignac2016].
Surprisingly, the correlation between the MBI score and DTL was positive and also large (`r cor_apa(cor.test(score_data$mbi, score_data$dtl, method = "spearman"), format = "rmarkdown")`).
The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.

`r Table2`

@@

  Table3 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  Table3[2:ncol(Table3)] <- format(round(Table3[2:ncol(Table3)], digits = 3), nsmall = 2)

  replication_table <-
    kbl(Table3,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

  Figure1 <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edgeLabels = fit_param, # specify the edge labels with the asterisks as previously created
                       edge.label.cex = 1, esize = 2, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

@@

In order to replicate findings by Grass et al. [-@Grass2018] we computed a multiple mediation model to investigate whether the association of NFC and reduced personal efficacy was partially mediated by self-control and habitual use of reappraisal and suppression, respectively.
The baseline model did not fit the data ($\chi$^2^(`r round(fit_summ$FIT[["baseline.df"]], digits = 0)`, $N=$ `r nrow(data)`) = `r round(fit_summ$FIT[["baseline.chisq"]], digits = 2)`, $p < .001$).
Applying the cutoffs by Hu and Bentler [-@Hu1999] to the fit indices of $CFI=$ `r round(fit_summ$FIT[["cfi"]], digits = 2)`, $TLI=$ `r round(fit_summ$FIT[["tli"]], digits = 2)`, $SRMR=$ `r round(fit_summ$FIT[["srmr"]], digits = 2)`, and $RMSEA=$ `r format(round(fit_summ$FIT[["rmsea"]], digits = 2), nsmall = 2)`, 95% $CI$ [`r round(fit_summ[["FIT"]][["rmsea.ci.lower"]], digits = 2)`,`r round(fit_summ[["FIT"]][["rmsea.ci.upper"]], digits = 2)`], suggested good fit of the proposed model throughout all indices.
Standardized estimates are displayed in **Figure**, total, direct, and indirect effects are listed in **Table**.
We could replicate a positive association of NFC and self control ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a1"], digits = 3)`), and a negative association of habitual reappraisal and reduced personal efficacy ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b2"], digits = 3)`).
However, we could neither replicate the effect of NFC on reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "b1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "b1"], digits = 3)`), nor the indirect effect of NFC on reduced personal efficacy via reappraisal ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect2"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect2"], digits = 3)`).
Furthermore, even though NFC and self control and reduced personal efficacy and self control were associated, the indirect effect of NFC on reduced personal efficacy via self control did not reach significance ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "Indirect1"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "Indirect1"], digits = 3)`).
Additionally, NFC was negatively associated with habitual use of suppression ($\beta=$ `r round(fit_summ$PE$std.all[fit_summ$PE$label == "a3"], digits = 2)`, $p=$ `r round(fit_summ$PE$pvalue[fit_summ$PE$label == "a3"], digits = 3)`), which was not the case in the study by Grass et al. [-@Grass2018].

@@

  Table4 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC and years spent teaching $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  Table4[2:ncol(Table4)] <- format(round(Table4[2:ncol(Table4)], digits = 3), nsmall = 2)

  replicationyears_table <-
    kbl(Table4,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 9, 11) %>%
    pack_rows("Total Effect", 12, 12) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```

@@

  Figure2 <- semPaths(fityears, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edge.label.cex = 1, esize = 2, # size specifications
                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       exoCov = FALSE, # do not plot covariance between exogenous variables
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

@@

  Figure3 <- semPaths(fit2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.position = c(0.6,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.3,0.6,0.3,0.5,0.55,0.4,0.5,0.6,0.45,0.5),
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```

```{r objective2_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  Table5[2:ncol(Table5)] <- format(round(Table5[2:ncol(Table5)], digits = 3), nsmall = 2)

  drrmodel_table <-
    kbl(Table5,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand Resource Fit, MBI = Maslach Burnout Inventory, NFC = Need for Cognition, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```
